--- 
title: <p style="font-size:40pt"> Governing Infrastructure </p>  
subtitle: <div align="top"> <p style="font-size:24pt">
    Mini-project Presentation 
    </p></div> 
author: "Nick Cuba, Pilar Delpino, Madelyn Rivera and Laura Sauls"
date: <p style="font-size:12pt"> 7/24/2020 </p>
output: 
  slidy_presentation:
    theme: "flatly" 
    footer: "SESYNC Cyber Institute 2020"
--- 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## <br/> Background

## <br/> Question and Data

## <br/> Results

## Ucayali Roads


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

